Is high social class always beneficial for survival? Northern Sweden 1801--2013

### 2018-02-13 article3c.Rmd
introduce new weights

```{r exweight}
exm <- vb0Tab[vb0Tab$period == "1901-1925" & vb0Tab$sex == "male", c("age", "civst", "urban", "exposure", "event", "hisclass")]
all <- aggregate(exm["exposure"], by = exm[c("civst", "urban")], FUN = sum)
all
```

@@

```{r forelite}
elite <- exm[exm$hisclass == "elite", c("age", "civst", "urban", "exposure", "event", "hisclass")]
el <- aggregate(elite["exposure"], by = elite[, c("civst", "urban")], FUN = sum)
el
```

The weights are now 'all$exposure / el$exposure`, that is

```{r wei}
all$wei <- all$exposure / el$exposure
all
```

@@

```{r puttog}
per1901 <- rbind(elite, middle, worker, farmer, non)
per1901$age <- factor(per1901$age)
```

Let us fit with and without weights. Without weights:

>>>>

```{r exweight}
exm <- vb0Tab[vb0Tab$period == "1901-1925" & vb0Tab$sex == "male", c("age", "civst", "urban", "exposure", "event", "hisclass")]
all <- aggregate(exm["exposure"], by = exm[c("civst", "urban", "age")], FUN = sum)
all
```

@@

```{r forelite}
elite <- exm[exm$hisclass == "elite", c("age", "civst", "urban", "exposure", "event", "hisclass")]
el <- aggregate(elite["exposure"], by = elite[, c("civst", "urban", "age")], FUN = sum)
el
```

The weights are now 'all["exposure"]" / el["exposure"]`, that is

```{r wei}
wei <-  all$exposure / el$exposure
all$wei <- wei 
all$Expos <- all$exposure * wei
all$Eve <- all$event * wei
all
```

@@

```{r puttog}
per1901 <- rbind(elite, middle, worker, farmer, non)
per1901$age <- factor(per1901$age)
#fit <- lm(exposure ~ civst * urban * age, data = per1901)
#pred <- predict(fit, type = "response")
#per1901$wght2 <- pred / per1901$exposure
```

Let us fit with and without weights. Without weights, see Figure \@ref(fig:testfit).
